Figures for Paper

### 2021-09-13 paper_figures.Rmd
Update paper_figures.Rmd

```{r}
boxplot_table %>%
  filter(!(tissue_clean %in% c("Cerebellum","Hippocampus","Occipital Cortex"))) %>%
  mutate(detected = inclusion_reads > 0) %>%
  dplyr::select(sample,disease_group2,detected,tissue_clean) %>%
  unique() %>%
  group_by(disease_group2,tissue_clean) %>%
  mutate(n_sample = n_distinct(sample)) %>%
  mutate(n_sample_detected = sum(detected)) %>%
  dplyr::select(tissue_clean,disease_group2,n_sample,n_sample_detected) %>%
  unique() %>%
  mutate(detection_rate = n_sample_detected / n_sample) %>%
  mutate(disease_group2 = gsub("Control"," Control",disease_group2)) %>%
  ungroup() %>%
  filter(grepl("ALS-TDP|FTLD-T",disease_group2)) %>%
  mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                    "Frontal Cortex",
                                    "Lumbar Spinal Cord",
                                    "Motor Cortex",
                                    "Thoracic Spinal Cord")) %>%
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )")) %>%
  mutate(cortex = ifelse(grepl(" Cord",tissue_clean),"cot","cor")) %>%
  ggplot() +
  geom_col(aes(x = detection_name, y = detection_rate,fill = detection_name),position = position_dodge2(width = 0.8, preserve = "single")) +
  ggpubr::theme_pubr() +
  ylab("Percent of Tissues \n UNC13A Cryptic Detected") +
  theme(text = element_text(size = 18)) +
  xlab("N tissues") +
  facet_wrap(~tissue_clean,scales = 'free_x',nrow = 3) +
    scale_y_continuous(lim = c(0,1),labels = scales::percent,expand = c(0,0) ) +
  theme(axis.text.x =  element_text(size = 14)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(text = element_text(size = 18))  +
  scale_fill_manual(values = c("#4C97B5","#4C97B5","#4C97B5","#4C97B5","#4C97B5","red","#C87156","#C87156")) +
  theme(legend.position = "none")
```

@@

peak_df <- filtered_df %>%
  ungroup() %>%
  group_by(pos) %>%
  mutate(max_at_pos = max(normalised_counts)) %>%  # at least 1 of the 4 samples above the threshold
  ungroup() %>%
  filter(max_at_pos >= peak_t) %>%  # at least 1 of the 4 samples above the threshold
  group_by(condition, pos) %>%
  mutate(peak_mean = mean(normalised_counts),
         peak_sd = sd(normalised_counts)) %>%
  ungroup() %>%
  select(condition, pos, peak_mean, peak_sd) %>%
  unique() %>%
  pivot_wider(names_from = "condition", values_from = c("peak_mean", "peak_sd")) %>%
  mutate(frac_increase = (peak_mean_R-peak_mean_H)/peak_mean_H) %>%
  mutate(peak_rank = rank(frac_increase)) %>%
  mutate(colour = ifelse(abs(pos-exon_snp)<region_length, "gold",
                         ifelse(abs(pos-intron_snp)<region_length, "purple", "grey50")))

@@

ggplot(peak_df, aes(x = peak_rank, y = 100*frac_increase, fill=colour)) +
  geom_bar(stat="identity") +
  scale_fill_identity() +
  theme_minimal() +
  ggpubr::theme_pubr()+
  ylab("% change in 2x Risk") +
  xlab("Rank") +
  geom_errorbar(aes(ymin = 100*lower_bound, ymax = 100*upper_bound, x = peak_rank),
                width = 0.3)

@@

```{r}
guide_strength = fread(file.path(here::here(),"data","different_guides_cryptic_expression.csv"))
guide_strength %>% 
  melt() %>% 
  filter(`cell line` == "i5W") %>% 
   mutate(condition = fct_relevel(condition,
                              "control","tdp43_mild")) %>%
    ggbarplot(,
              x = "condition",
              add = c("mean_se","jitter"),
              y = "value",
              fill = 'variable',
              color = 'variable',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
      scale_color_manual(
        values = c("#1C2617","#262114","#262114")
    ) +
        scale_fill_manual(
        values = c("#1576b8","#eb7f3f","#975452")
    ) +
    scale_y_continuous(labels = scales::percent) +
  ggtitle("NCRM5")

guide_strength %>% 
  melt() %>% 
  filter(`cell line` == "i11w_repeat") %>% 
   mutate(condition = fct_relevel(condition,
                              "control","tdp43_mild")) %>%
    ggbarplot(,
              x = "condition",
              add = c("mean_se","jitter"),
              y = "value",
              fill = 'variable',
              color = 'variable',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
      scale_color_manual(
        values = c("#1C2617","#262114","#262114")
    ) +
        scale_fill_manual(
        values = c("#1576b8","#eb7f3f","#975452")
    ) +
    scale_y_continuous(labels = scales::percent) +
  ggtitle("WTC11")
```

>>>>

```{r}
boxplot_table %>%
  filter(!(tissue_clean %in% c("Cerebellum","Hippocampus","Occipital Cortex"))) %>%
  mutate(detected = inclusion_reads > 0) %>%
  dplyr::select(sample,disease_group2,detected,tissue_clean) %>%
  unique() %>%
  group_by(disease_group2,tissue_clean) %>%
  mutate(n_sample = n_distinct(sample)) %>%
  mutate(n_sample_detected = sum(detected)) %>%
  dplyr::select(tissue_clean,disease_group2,n_sample,n_sample_detected) %>%
  unique() %>%
  mutate(detection_rate = n_sample_detected / n_sample) %>%
  mutate(disease_group2 = gsub("Control"," Control",disease_group2)) %>%
  ungroup() %>%
  filter(grepl("ALS-TDP|FTLD-T",disease_group2)) %>%
  mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                    "Frontal Cortex",
                                    "Lumbar Spinal Cord",
                                    "Motor Cortex",
                                    "Thoracic Spinal Cord")) %>%
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )")) %>%
  mutate(cortex = ifelse(grepl(" Cord",tissue_clean),"cot","cor")) %>%
  ggplot() +
  geom_col(aes(x = detection_name,
               y = detection_rate,
               fill = detection_name),color = 'black',position = position_dodge2(width = 0.8, preserve = "single")) +
  ggpubr::theme_pubr() +
  ylab("Percent of Tissues \n UNC13A Cryptic Detected") +
  theme(text = element_text(size = 18)) +
  xlab("N tissues") +
  facet_wrap(~tissue_clean,scales = 'free_x',nrow = 3) +
    scale_y_continuous(lim = c(0,1),labels = scales::percent,expand = c(0,0) ) +
  theme(axis.text.x =  element_text(size = 14)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(text = element_text(size = 18))  +
  scale_fill_manual(values = c("#00bd7dff","#00bd7dff","#00bd7dff","#00bd7dff","#00bd7dff","red","#e668f3ff","#e668f3ff")) +
  theme(legend.position = "none")
```

@@

peak_df <- filtered_df %>%
  ungroup() %>%
  group_by(pos) %>%
  mutate(max_at_pos = max(normalised_counts)) %>%  # at least 1 of the 4 samples above the threshold
  ungroup() %>%
  filter(max_at_pos >= peak_t) %>%  # at least 1 of the 4 samples above the threshold
  group_by(condition, pos) %>%
  mutate(peak_mean = mean(normalised_counts),
         peak_sd = sd(normalised_counts)) %>%
  ungroup() %>%
  select(condition, pos, peak_mean, peak_sd) %>%
  unique() %>%
  pivot_wider(names_from = "condition", values_from = c("peak_mean", "peak_sd")) %>%
  mutate(frac_increase = (peak_mean_R-peak_mean_H)/peak_mean_H) %>%
  mutate(peak_rank = rank(frac_increase)) %>%
  mutate(colour = ifelse(abs(pos-exon_snp)<region_length, "#f7e7abff",
                         ifelse(abs(pos-intron_snp)<region_length, "#c8e1c4ff", "grey50")))

@@

ggplot(peak_df, aes(x = peak_rank, y = 100*frac_increase, fill=colour)) +
  geom_bar(stat="identity",,color = 'black') +
  scale_fill_identity() +
  theme_minimal() +
  ggpubr::theme_pubr()+
  ylab("% change in 2x Risk") +
  xlab("Rank") +
  geom_errorbar(aes(ymin = 100*lower_bound, ymax = 100*upper_bound, x = peak_rank),
                width = 0.3,size = 1.1)

@@

```{r}
guide_strength = fread(file.path(here::here(),"data","different_guides_cryptic_expression.csv"))

guide_strength %>% 
  melt() %>% 
  filter(`cell line` == "i5W") %>% 
   mutate(condition = fct_relevel(condition,
                              "control","tdp43_mild")) %>%
    ggbarplot(,
              x = "condition",
              add = c("mean_se","jitter"),
              y = "value",
              fill = 'variable',
              color = 'variable',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
      scale_color_manual(
        values = c("#1C2617","#262114","#262114")
    ) +
        scale_fill_manual(
        values = c("#1576b8","#eb7f3f","#975452")
    ) +
    scale_y_continuous(labels = scales::percent) +
  ggtitle("NCRM5") +
         theme(axis.line = element_line(colour = 'black', size = 1.5),
        axis.ticks = element_line(colour = "black", size = 2))

guide_strength %>% 
  melt() %>% 
  filter(`cell line` == "i11w_repeat") %>% 
   mutate(condition = fct_relevel(condition,
                              "control","tdp43_mild")) %>%
    ggbarplot(,
              x = "condition",
              add = c("mean_se","jitter"),
              y = "value",
              fill = 'variable',
              color = 'variable',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
      scale_color_manual(
        values = c("#1C2617","#262114","#262114")
    ) +
        scale_fill_manual(
        values = c("#1576b8","#eb7f3f","#975452")
    ) +
    scale_y_continuous(labels = scales::percent) +
  ggtitle("WTC11") +
          axis.line = element_line(colour = 'black', size = 1.5),
        axis.ticks = element_line(colour = "black", size = 2))
```
